Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-10-01 ms.tex
added a sentence in the abstract about WISE infrared excess.

\begin{abstract}
KIC 12557548 b is first of a growing class of intriguing disintegrating planet candidates, which lose mass in the form of \added{a metal rich vapor that condenses into} dust particles escaping their surface.
Here, we follow up two perplexing observations of the system: 1) the transits appeared shallower than average in 2013 and 2014 and 2) the parameters derived from a high resolution spectrum of the star differed from other results using photometry and low resolution spectroscopy.
We observe 5 transits of the system with the 61-inch Kuiper telescope in 2016 and show that they are consistent with photometry from the \kepler\ spacecraft in 2009-2013.
We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4440 $\pm$70 K star in agreement with the photometry and low resolution spectroscopy.
This disfavors the hypothesis that planet disintegration affected the analysis of prior high resolution spectra of this star.
We apply Principal Component Analysis to the \kepler\ long cadence data to understand the modes of disintegration.
There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism on such long timescales remains unclear.
\end{abstract}

@@

While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of a \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
This is also true of the disintegrating system K2-22 b.
These infrared fluxes may arise from dust created by the disintegrating planet and pushed out to a larger radius to form a disk or ring.
Further investigation of the infrared excesses should be explored observationally and theoretically.

>>>>

\begin{abstract}
KIC 12557548 b is first of a growing class of intriguing disintegrating planet candidates, which lose mass in the form of \added{a metal rich vapor that condenses into} dust particles escaping their surface.
Here, we follow up two perplexing observations of the system: 1) the transits appeared shallower than average in 2013 and 2014 and 2) the parameters derived from a high resolution spectrum of the star differed from other results using photometry and low resolution spectroscopy.
We observe 5 transits of the system with the 61-inch Kuiper telescope in 2016 and show that they are consistent with photometry from the \kepler\ spacecraft in 2009-2013.
We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find them to be consistent with a main-sequence T$_{eff}$=4440 $\pm$70 K star in agreement with the photometry and low resolution spectroscopy.
This disfavors the hypothesis that planet disintegration affected the analysis of prior high resolution spectra of this star.
We apply Principal Component Analysis to the \kepler\ long cadence data to understand the modes of disintegration.
There is a tentative 491 day periodicity of the second principal component, which corresponds to possible long-term evolution of the dust grain sizes, though the mechanism on such long timescales remains unclear.
\added{Another area to be explored is the WISE band 3 and 4 infrared excess in the spectral energy distribution, probably arising for a dust ring or disk.}
\end{abstract}

@@

While examining the bolometric flux from all available data, we notice that the WISE band 3 and 4 fluxes at 12 $\mu$m and 22 $\mu$m \citep{wright2010wise} are significantly in excess of a \citet{castelli2004models} stellar model, as shown in Figure \ref{fig:SED}.
This is also true of the disintegrating system K2-22 b.
These infrared fluxes may arise from dust created by the disintegrating planet and radiatively pushed out to a larger radius to form a disk or ring.
Further investigation of the infrared excesses should be explored observationally and theoretically.
